Meshpoint optimization

### 2022-05-13 notes/optimizing-meshpoints.Rmd
rename files to remove spaces

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(metRology)
library(targets)
library(ipmr)

@@

```{r data, echo=TRUE}
withr::with_dir(here::here(), {
  tar_load(vit_list_det_ff)
  tar_load(vit_list_stoch_ff)
})
```

@@

```{r}
proto_det <- make_proto_ipm_det(vit_list_det_ff)
```

@@

plot(x =seq(20, 150, 5), y = lambdas_det, ylab = "lambda", xlab = "meshpoints")
```

@@

```{r}
proto_stoch <- make_proto_ipm_stoch(vit_list_stoch_ff)
```

```{r}
year_seq <- sample(2000:2009, 100, replace = TRUE)

proto_stoch_list <- 
  seq(60, 120, 10) %>%
  map(~{
    proto_stoch %>% 
    define_domains(log_size = c(0, 8.018296, .x)) %>%  
    #arbitrary starting population state
    define_pop_state(n_log_size = runif(.x), n_sdlg = .1)
  })

# make_ipm(proto_stoch_list[[1]],
#          iterations = 100,
#          kernel_seq = year_seq,
#          usr_funs = list(get_scat_params = get_scat_params))
```

### Note:

This currently isn't working because of a bug in `ipmr` that causes `make_ipm()` to hang when `kernel_seq` is supplied <https://github.com/levisc8/ipmr/issues/58>

```{r eval=FALSE}
lambdas_stoch <-
  proto_stoch_list %>%
  map_dbl( ~ make_ipm(
    .x,
    iterations = 100,
    kernel_seq = year_seq,
    usr_funs = list(get_scat_params = get_scat_params, coef = coef)
  ) %>% lambda(log = FALSE))

plot(x = seq(60, 120, 10), y = lambdas_stoch, ylab = "stochastic lambda", xlab = "meshpoints")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(tidyverse)
library(here)
library(metRology)
library(targets)
library(ipmr)

@@

```{r data, echo=TRUE}
withr::with_dir(here::here(), {
  tar_load(vit_list_det_ff)
  tar_load(vit_list_stoch_ff)
  tar_load(pop_vec_ff)
})
```

@@

```{r}
proto_det <- make_proto_ipm_det(vit_list_det_ff, pop_vec = pop_vec_ff)
```

@@

plot(x =seq(20, 150, 5), y = lambdas_det, ylab = "lambda", xlab = "meshpoints")
plot(x = seq(20, 150, 5), y = lambdas_det - lag(lambdas_det), ylab = "∆lambda", xlab = "meshpoints")
```

@@

```{r}
proto_stoch <- make_proto_ipm_stoch(vit_list_stoch_ff, pop_vec = pop_vec_ff)
```

```{r}
proto_stoch_list <- 
  seq(20, 140, 10) %>%
  map(~{
    proto_stoch %>% 
    define_domains(log_size = c(0, 8.018296, .x)) %>%  
    #replace starting pop vector with uniform one with correct number of meshpts
    define_pop_state(n_log_size = rep(1/(.x + 1), .x), n_sdlg = 1/.x)
  })
```

```{r}
year_seq <- sample(2000:2009, 1000, replace = TRUE)

ipm_list <-
  proto_stoch_list %>%
  map( ~ make_ipm(
    .x,
    iterations = 1000,
    kernel_seq = year_seq,
    usr_funs = list(get_scat_params = get_scat_params)
  ))

lambdas_stoch <- ipm_list %>% map_dbl(~lambda(.x, log = FALSE))

plot(x = seq(20, 140, 10), y = lambdas_stoch, ylab = "stochastic lambda", xlab = "meshpoints")
plot(x = seq(20, 140, 10), y = lambdas_stoch - lag(lambdas_stoch), ylab = "∆lambda", xlab = "meshpoints")
```

Ok, looks about the same for the stochastic model, which makes sense.
